Carryover effects in free recall reveal how prior experiences influence memories of new experiences

### 2023-01-06 paper/main.tex
- finished "random conditions" description - added bryan as a co-author (yay!) - working on description of order manipulation conditions

\title{Carryover effects in free recall reveal how prior experiences influence memories of new experiences}
\author{Jeremy R. Manning\textsuperscript{1, *}, Kirsten Ziman\textsuperscript{1, 2}, Emily Whitaker\textsuperscript{1},\\Paxton C. Fitzpatrick\textsuperscript{1}, Madeline R. Lee\textsuperscript{1}, and Andrew C. Heusser\textsuperscript{1, 3}\\\textsuperscript{1}Dartmouth College\\\textsuperscript{2}Princeton University\\\textsuperscript{3}Akili Interactive\\\textsuperscript{*}Corresponding author: jeremy.r.manning@dartmouth.edu}

@@

The above assignments of words to lists was performed once across all
participants, such that every participant studied the same set of 16 lists. We
randomized the study order of these lists across participants. For participants
in some conditions, on some lists, we also randomly varied two additional
visual features to each word: the presentation font color, and the word's
onscreen location. These attributes were assigned independently for word (and
for every participant) at the times the words were displayed onscreen. These
visual features were varied for words in all lists and conditions except for
the ``reduced'' condition (all lists), the first eight lists of the ``reduced
(early)'' condition, and the last eight lists of the ``reduced (late)''
condition. In these latter cases, words were all presented in black at the
center of the experimental computer's display.

@@

@@

\subsubsection*{Random conditions}

We used four ``control'' conditions to evaluate and explore participants'
baseline behaviors. We also used performance on these control conditions to
help interpret performance in other ``manipulation'' conditions. Two control
conditions served as ``anchorpoints.'' In the first anchorpoint condition,
which we call the \textit{feature rich} condition, we randomly shuffled the
presentation order (independently for each participant) of the words on each
list. The second anchorpoint condition

\subsubsection*{Order manipulation conditions}

>>>>

\title{Carryover effects in free recall reveal how prior experiences influence
memories of new experiences}

\author{Jeremy R. Manning\textsuperscript{1, *}, Kirsten
Ziman\textsuperscript{1, 2}, Emily Whitaker\textsuperscript{1},\\Paxton C.
Fitzpatrick\textsuperscript{1}, Madeline R. Lee\textsuperscript{1}, Bryan J.
Bollinger\textsuperscript{1},\\and Andrew C. Heusser\textsuperscript{1,
3}\\\textsuperscript{1}Dartmouth College\\\textsuperscript{2}Princeton
University\\\textsuperscript{3}Akili
Interactive\\\textsuperscript{*}Corresponding author:
jeremy.r.manning@dartmouth.edu}

@@

The above assignments of words to lists was performed once across all
participants, such that every participant studied the same set of 16 lists. In
every condition we randomized the study order of these lists across
participants. For participants in some conditions, on some lists, we also
randomly varied two additional visual features to each word: the presentation
font color, and the word's onscreen location. These attributes were assigned
independently for word (and for every participant) at the times the words were
displayed onscreen. These visual features were varied for words in all lists
and conditions except for the ``reduced'' condition (all lists), the first
eight lists of the ``reduced (early)'' condition, and the last eight lists of
the ``reduced (late)'' condition. In these latter cases, words were all
presented in black at the center of the experimental computer's display.

@@

Most of the experimental manipulations we carried out entailed presenting or
sorting the presented words differently on the first eight lists participants
studied (which we call \textit{early} lists) versus on the final eight lists
they studied (\textit{late} lists). Since every participant studied exactly 16
lists, using this terminology every list was either ``early'' or ``late''
depending on its order in the list study sequence.

@@

\subsubsection*{Random conditions (Fig.~\ref{fig:exp}, top four rows)}

We used four ``control'' conditions to evaluate and explore participants'
baseline behaviors. We also used performance on these control conditions to
help interpret performance in other ``manipulation'' conditions. Two control
conditions served as ``anchorpoints.'' In the first anchorpoint condition,
which we call the \textit{feature rich} condition, we randomly shuffled the
presentation order (independently for each participant) of the words on each
list. In the second anchorpoint condition, which we call the \textit{reduced}
condition, we randomized word presentations as in the feature rich condition.
However, rather than assigning each word a random color and location, we
instead displayed all of the words in black and at the center of the screen.

In the \textit{reduced (early)} condition, we followed the ``reduced''
procedure (presenting each word in black at the center of the screen) for early
lists, and followed the ``feature rich'' procedure (presenting each word in a
random color and location) for late lists. Finally, in the \textit{reduced
(late)} condition, we followed the feature rich procedure for earlylists and
the reduced procedure for late lists.

\subsubsection*{Order manipulation conditions (Fig.~\ref{fig:exp}, middle six
rows)}

Each of six \textit{order manipulation} conditions used a different
feature-based sorting procedure to order words on early lists, where each
sorting procedure relied on one feature dimension. On late lists, the words
were always presented in a randomized order (chosen anew for each participant).
In all of the order manipulation conditions, we varied words' font colors and
onscreen locations, as in the feature rich condition.
